High-level cognition is supported by information-rich but compressible brain activity patterns

### 2024-02-13 paper/main.tex
adding autocorrelation analysis (will remove later)

One potential limitation of our work concerns how our measure of
informativeness might generalize across different tasks, cognitive
representations, and processes. Our use of across-participant temporal decoding
accuracy as a proxy for informativeness is motivated in part by prior work that
introduced across-participant similarity (in time-varying response to a
stimulus) as a means of identifying stimulus-driven brain activity
patterns~\citep{SimoEtal16}. Intuitively, only activity patterns that are
driven by the stimulus would be expected to synchronize (i.e., be time-locked
to the stimulus) across participants. This approach implicitly removes
idiosyncratic responses (e.g., neural patterns that are \textit{not} similar
across people). However, there are also some published examples, including in
our own prior work, that indicate that some types of stimulus-evoked activity
will be missed by across-participant comparisons. For example we have reported
how brain regions like the ventromedial prefrontal cortex (vmPFC) show
stimulus-driven responses that are, for the most part, \textit{not} similar
across people. In that paper (and drawing on other work), we suggest that the
vmPFC seems to represent or support highly idiosyncratic internal states, like
affective responses. Although we would consider the vmPFC to be a
``high-level'' region (e.g., we consider affect to be a relatively high-level
aspect of cognition), the measure of informativeness that we used in our
current study would identify regions like the vmPFC as having \textit{low}
informativeness. This is because across-participant decoding accuracy (our
proxy measure for informativeness) will only be high for representations or
responses that are common across people.

>>>>

One potential limitation of our work concerns how our measure of
informativeness might generalize across different tasks, cognitive
representations, and processes. Our use of across-participant temporal decoding
accuracy as a proxy for informativeness is motivated in part by prior work that
introduced across-participant similarity (in time-varying response to a
stimulus) as a means of identifying stimulus-driven brain activity
patterns~\citep{SimoEtal16}. Intuitively, only activity patterns that are
driven by the stimulus would be expected to synchronize (i.e., be time-locked
to the stimulus) across participants. This approach implicitly removes
idiosyncratic responses (e.g., neural patterns that are \textit{not} similar
across people). However, there are also some published examples, including in
our own prior work, that indicate that some types of stimulus-evoked activity
will be missed by across-participant comparisons. For example we have reported
how brain regions like the ventromedial prefrontal cortex (vmPFC) show
stimulus-driven responses that are, for the most part, \textit{not} similar
across people~\citep{ChanEtal21a}. In that paper (and drawing on other work), we suggest that the
vmPFC seems to represent or support highly idiosyncratic internal states, like
affective responses. Although we would consider the vmPFC to be a
``high-level'' region (e.g., we consider affect to be a relatively high-level
aspect of cognition), the measure of informativeness that we used in our
current study would identify regions like the vmPFC as having \textit{low}
informativeness. This is because across-participant decoding accuracy (our
proxy measure for informativeness) will only be high for representations or
responses that are common across people.
